An Overview of Distributed Version Control Systems

### 2010-06-08 laarsample.tex
Agregado un párrafo con el plugin de eclipse

>>>>

The plugin to integrate Git with Eclipse is still under major development so it only allows the most basic features to be used.
Unfortunately, as the time this paper is being written, it is not yet mature enough to be used frequently as it usually forgets configurations. For instance, it cannot remember which repository to push, so each time the developer wants to push some changesets a custom repository must be specified again.
